RSA + Scalar implicature / TBD

### 2015-11-10 models/RSA+AmbiguousSemantics.Rmd
updated writeup

## Literal listener studies

@@

`scale`: The scale we're currently investigating (i.e. `good_excellent`).

@@

<center>
<img src="RSA+AmbiguousSemantics_Images/e11_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
</center>
```{r}
#![alt text](RSA+AmbiguousSemantics_Images/e11_example.png)
```

>>>>

## Literal listener studies
<center>
<img src="RSA+AmbiguousSemantics_Images/literal_listener_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
</center>

@@

`scale`: The scale we're currently investigating (i.e. "good_excellent").

@@

<center>
<img src="RSA+AmbiguousSemantics_Images/prag_listener_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
</center>
